Decomposing labelled proof theory for~intuitionistic~modal~logic

### 2020-08-18 FullyLabelled/JLC/reviews/notes.tex
small modif

\begin{center}
	$\vlderivation{
		\vlin{\rlabrn\BOX}
		{}
		{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}
		{\vlin{\rlabrn\IMP}{\lb w\mbox{ fresh}}
			{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}
			{\vlin{\rn F_1}{\lb u\mbox{ fresh}}
				{\futs xy, \futs zw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
				{\vlin{\rn g_{1100}}{\exists \lb{w'}, \lb{w''}}
					{\futs xy, \futs zw, \futs yu, \accs uw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
					{\vlin{\llabrn\BOX}{}
						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
						{\vlin{}{}
							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A}, \labels{w''}{A} \SEQ \labels{w}{A}}
							{}}}}}}
	}$
\end{center}

>>>>

\begin{center}
	$\vlderivation{
		\vlin{\rlabrn\BOX}
		{}
		{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}
		{\vlin{\rlabrn\IMP}{\lb w\mbox{ fresh}}
			{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}
			{\vlin{\rn F_1}{\lb u\mbox{ fresh}}
				{\futs xy, \futs zw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
				{\vlin{\rn g_{1011}}{ \lb{w'}\mbox{ fresh}}
					{\futs xy, \futs zw, \futs yu, \accs uw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
					{\vlin{\llabrn\BOX+\rn{refl}}{}
						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w}{w'}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
						{\vlin{}{}
							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w}{w'}, \accs yz, \labels{w}{\BOX A}, \labels{w'}{A} \SEQ \labels{w}{A}}
							{}}}}}}
	}$
\end{center}
